%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Skills/Tools: JavaScript, MagicMirror$^2$ - https://github.com/bryngo/MagicMirror} % Affiliation/role
  {Magic Mirror \textcolor{lightgray}{| Add Some Tech to your Morning Routine}} % Organization/group
  {} % Location
  {Jul 2017 - Present} % Date(s)
  {
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Built an interactive magic mirror powered by a Raspberry Pi.}
    \item {Enabled users to see the weather, read the news, and more - all without using a mobile device.}
    \item {Contributed an open source slideshow module to the developer community.}
  \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Skills/Tools: Java - https://github.com/bryngo/LeagueReportCard} % Affiliation/role
  {League Report Card \textcolor{lightgray}{| Play Smarter}} % Organization/group
  {} % Location
  {Apr 2017 - May 2017} % Date(s)
  {
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Implemented a match summary reporter using, Orianna, a Java wrapper for the Riot Games API V2.}
    \item {Writes data to a csv file to be read into data visualizations.}
  \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Skills/Tools: Swift, SpriteKit - https://github.com/bryngo/Visu-rithm} % Affiliation/role
  {Visu-rithm (HackDavis) \textcolor{lightgray}{| Visual Algorithms for the Curious Programmer}} % Organization/group
  {} % Location
  {Jan 2017} % Date(s)
  {
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Implemented an insertion sort visualization for iOS using SpriteKit to help new programmers understand basic algorithms.}
  \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Skills/Tools: Python, Jinja - https://github.com/bryngo/TravelBuddy} % Affiliation/role
  {TravelBuddy (CalHacks) \textcolor{lightgray}{| Visual Algorithms for the Curious Programmer}} % Organization/group
  {} % Location
  {October 2017} % Date(s)
  {
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Used the Google Vision, Google Maps, and Wikipedia API to implement a reverse search application for finding nearby restaurants.}
    \item {Users can upload photos of food to learn about the history and where to buy it.}
  \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
